---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 
```{r}
library(lubridate)
library(stringr)
library(tidyverse)
library(RVerbalExpressions)
```

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
current_year <- as.character(year(today()))
ymd(str_c(current_year, "-1-1")) + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
get_age <- function(date){
  (date %--% today())  %/% years(1)
}

get_age(ymd("1996-10-15"))
```


Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
get_wday_b <- function(date){
  wday(date)
}

get_wday_b(ymd("1996-10-15"))

```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
str_view(words, ".......", match = TRUE)
```


```{r}
has_more_than_7 <- rx() %>% 
  rx_start_of_line() %>% 
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  rx_end_of_line() %>% 
  print()

str_detect(words,has_more_than_7, match = T)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)


```{r That only contain consonants.}
str_detect(words, "^[^aeiou]+$")
```


```{r}
not_vowels<- rx() %>% 
  rx_start_of_line() %>% 
  rx_something_but("aeiou") %>% 
  rx_end_of_line() %>% 
  print()

str_detect(words, not_vowels)
```



Empirically verify the rule “i before e except after c”

```{r Empirically verify the rule “i before e except after c”}
length(str_subset(words, "(cei|[^c]ie)"))
length(str_subset(words, "(cie|[^c]ei)"))
```


```{r}
rule_ic <- rx() %>% 
  rx_anything_but("c") %>% 
  rx_find("i") %>% 
  rx_find("e") %>% 
  print()

str_detect(words, rule_ic)
```



Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r phone number}
str_detect(x, "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d")
```



# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

